
\def\meshpos{\textbf{p}}
\def\templatepos{\textbf{a}}

\chapter[Online Tracking]{Online Tracking}
\label{ChapterOnlineTracking}

\section{Introduction}

\section{Related Research}

\subsection{Boston Head Pose Corpus}

\section{Description of System}

\subsection{Initialisation}

\subsection{Head Pose Estimation by LM}
\label{SectionLmHeadPose}

Original idea: \cite{Liu2000}

\begin{equation}
\mathcal{F}(\textbf{R},\textbf{t}) = \displaystyle\sum_{i=1}^{\numFeatures} { ||\textbf{\templatepos}_{i} - proj(\textbf{R} \textbf{\meshpos}_i + \textbf{t})||^2 }
\label {LmPoseEquation}
\end{equation}

\subsection{Online Learning}

\subsection{Tracking with Multiple Templates}

\subsection{Estimate pose using Weighted RANSAC LM}

\subsection{Update tracker positions}

\section{Experimental Results}

\subsection{Head Pose Estimation}

\subsection{Facial Feature Tracking on Boston}

\subsection{Facial Feature Tracking on TwoTalk?}

\thesiscomment{Do we need to do these experiments?}

\section{Discussion}

\thesisstatement{Some features accurately track over a wider pose range than others}

\thesisstatement{Banks of pose specific head trackers can be used to extend the pose range that can be accurately tracked.}

\thesisstatement{The proposed online learning system can track faces accurately over a wide range of poses for smooth head motion.}

\thesisstatement{Poor initialisation of head pose in the online tracking system, often caused by difference face shapes, causes poor performance throughout the video.}

\thesisstatement{Online tracking system works on smooth motion sequences (Boston) but fails on unconstrained video.}

Why we don't use online tracking system later in the thesis?

\thesisstatement{LP Flocks are better than Online Tracker for TwoTalk videos.}


\section{Conclusions}

DISCUSS: Say how this is still an unsolved problem and neither this nor LPs fully address it
